\section*{Data Management Plan}

The team will disseminate the results of the proposed work through publications in peer-reviewed scientific journals, books, and peer-reviewed conference proceedings written in English.

The proposed research will produce a variety of data types: simulation, and optimization software; simulated datasets; measurements of physical objects; optical setup designs and calibration procedures and software; tutorials and instructional material. Both participating universities, University of California at Berkeley, and the Technion - Israel Institute of Technology, have policies encouraging release of all these data types. We will strive to make all data available to the research community and the general public. To achieve this, we discuss below  plans specific to the different data types created by this project.

\subsection*{Simulation and optimization software}

Software will take the form of large-scale simulation libraries, code interfacing with existing optimization libraries, as well as code interface with existing simulation packages for data generation. Development and storage will be performed using local repositories (git, mercurial, svn) with version control, issue tracking, and milestone planning. Collaborators will be given full access to these repositories during the execution of individual projects within the scope of the proposal. 

Upon completion of each project, the repositories will be cloned to online code sharing services (Github) and be released, under an appropriate open-source, copy-left license. Terms of use for these software products will include requirements of attribution and disclaimers of liability.

\subsection*{Optical setup designs}

Optical setups constructed as part of this project will be documented in terms of CAD designs and lists of components needed to construct them. Each setup will also include detailed guidelines for alignment, as well as software for calibration and operation. These resources will be stored and made available following the same guidelines as for software, as described in the previous subsection.

\subsection*{Simulated and measured data}

Generated and collected datasets will be stored locally for the duration of each individual project from this proposal, and will be distributed to collaborators for the duration of the respective projects. Datasets will include documentation detailing how they were generated or captured, and how they can be used.

Upon completion, this data will be released using both online hosting services (Amazon S3), as well as through the team members' academic websites, stored locally at their respective institutions with appropriate redundant back-up mechanisms to avoid data loss. Access to this data will be provided under terms of use including requirements of attribution and disclaimers of liability.

\subsection*{Instructional materials and tutorials}

The main products of the proposed research in this category will be particular projects, homework problems, and tutorial presentations associated with both course development and broader outreach. These educational materials will be released online at the appropriate websites of each PI's  home institution (course listings, websites dedicated to specific outreach programs).

\subsection*{Local storage}

For each of the above items, local storage will be provided by the computing facilities of the corresponding hosting institution. Both participating universities offer options for secure, long-term data storage, with automated, daily, and redundant backups. Additional backups will be stored locally in daily backed-up servers at each PI's laboratory.

\subsection*{Preserving data}  

The data will be preserved for the forseeable future (at least 10 years). After that period, the PIs will assess interest in the dataset based on the rate of download of the datasets.  The servers hosting the data will be maintained at Berkeley, even if the PIs are on sabbatical or leave. 

\subsection*{Intellectual property}

In the event that discoveries or inventions are made in direct connection to software or data produced as part of this proposed research, public access to this sources will be granted only after invention disclosures and patent filings have been completed.


%\section*{Mentoring Plan}
